COG-ED Manuscript

### 2021-10-18 06_Paper/COG-ED/Manuscript.Rmd
implemented rmANOVA with linear contrasts

  knitr::opts_chunk$set(echo = TRUE)
  library(bibtex)
  library(here)         # to set a directory without defined paths, "here" package
  library(tidyverse)    # plotting and managing data, "tidyverse" package
  library(bayestestR)   # computing area under the curve, "bayestestR" package
  library(papaja)       # APA conform output, "papaja" package
  library(nlme)         # fitting nonlinear mixed-effects model
  library(ez)           # compute repeated measures ANOVA
  # we will add the package versions before submission

@@

  # ANOVA with three linear contrasts, contrasting the d’ of two n-back levels (2,3,4) at a time
  # FIXME:  actually, I guess, we have a rmANOVA here as we look at repeated measures of a subject's reaction time 
  #         under different load levels (= time points), see below

@@

      contrasts(h1a_data$level) <- cbind(c(1,-1,0), c(0,1,-1), c(1,0,-1))     # there are predefined contrasts that may fit like contr.sum(3); contr.treatment(); contr.poly()

@@

      hypothesis1a_anova <- summary(aov(h1a_data$d ~ h1a_data$level))         # this calculates ANOVA without the specified contrasts and might be redundant
      hypothesis1a_anova.lm <- summary.lm(aov(h1a_data$d ~ h1a_data$level))   # this gives you the contrasted result
      hypothesis1a_posthoc <- TukeyHSD(aov(h1a_data$d ~ h1a_data$level))      # post hoc analyses should be redundant as we already contrasted the levels

  # FIXME:  rmANOVA
      h1a_data$subject <- factor(h1a_data$subject)
      # if there are reasonable concerns that we have NAs within our data set, we need to exclude this data beforehand

      # https://stackoverflow.com/questions/35891062/planned-contrasts-using-ezanova-output-in-r
      # set orthogonal contrasts
      options(contrasts = c("contr.sum", "contr.poly"))
      hypothesis1a_rmanova <- ezANOVA(h1a_data, dv = d, wid = subject, within = level, type = 3, return_aov = T) 
      # I propose to use type-III sums of squares even if we do have a balanced design, but we may discuss that. 
      # alternatively we could use afex, results might be plotted easier; it is also possible to set up a linear model
      # TODO: find a way to plot means
        # if Mauchly's Test for Sphericity is sign > report Greenhouse-Geisser Epsilon (GGe) or Huynh-Feldt-Epsilon (HFe)

      # get emmeans
      library(emmeans)
      # this only works without the manually defined contrasts in line 439
      hypothesis1a_emm <- emmeans(hypothesis1a_rmanova$aov, ~ level) 
      # these means should be used for reporting/ plotting the means per load level

      # get the contrasts
      pairs(hypothesis1a_emm, adjust = "Holm")
      # or
      contrast(hypothesis1a_emm, list(c1 = c(1,-1,0), c2 = c(1,0,-1), c3 = c(0,1,-1)))

      # alternatively, post hoc tests can be run
      # as we have 3 levels in factor load level, we would run a fisher's least significant differences (FLSD)
      hypothesis1a_fisher <- ezStats(h1a_data, dv = d, wid = subject, within = level, type = 3)
      # calculate and save mean differences
      p1.p2 <- hypothesis1a_fisher$Mean[1] - hypothesis1a_fisher$Mean[2]
      p1.p3 <- hypothesis1a_fisher$Mean[1] - hypothesis1a_fisher$Mean[3]
      p2.p3 <- hypothesis1a_fisher$Mean[2] - hypothesis1a_fisher$Mean[3]

      #if absolute value is higher than fsld, the pairwise comparison is significant
      abs(p1.p2) > hypothesis1a_fisher$FLSD[1]
      abs(p1.p3) > hypothesis1a_fisher$FLSD[1]   
      abs(p2.p3) > hypothesis1a_fisher$FLSD[1]

>>>>

  knitr::opts_chunk$set(echo = TRUE)
  library(bibtex)
  library(here)         # to set a directory without defined paths, "here" package
  library(tidyverse)    # plotting and managing data, "tidyverse" package
  library(bayestestR)   # computing area under the curve, "bayestestR" package
  library(papaja)       # APA conform output, "papaja" package
  library(nlme)         # fitting nonlinear mixed-effects model
  library(ez)           # compute repeated measures ANOVA
  library(emmeans)      # for custom contrasts in ANOVAs

  # we will add the package versions before submission

@@

  # repeated measures ANOVA with three linear contrasts, contrasting the d’ of two n-back levels (2,3,4) at a time

@@

@@

      hypothesis1a_rmanova <- afex::aov_ez(data = h1a_data,
                                           dv = "d",
                                           id = "subject",
                                           within = "level",
                                           type = 3,
                                           include_aov = TRUE)

      # specify contrasts

      hypothesis1a_emm <- emmeans(object = hypothesis1a_rmanova$aov,
                                  specs = "level")
      hypothesis1a_contrasts <- pairs(hypothesis1a_emm)

      # remove the temporary variable
